---
title: "Analyzing the effects of Neighborhood Crime Rate in the Great Toronto Area"
author: "Xu Yang"
date: "19/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Code and Data

# Keywords
Neighborhood Crime Rate, Logistic regression, Assault, Auto Theft, Break and Enter, Homicide, Robbery, Theft Over
```{r echo=FALSE}
library(opendatatoronto)
library(dplyr)
library(sf)
 
# get package
package <- show_package("fc4d95a6-591f-411f-af17-327e6c5d03c7")
package
 
# get all resources for this package
resources <- list_package_resources("fc4d95a6-591f-411f-af17-327e6c5d03c7")
 
# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
 
# load the first datastore resource as a sample
neighbourhoodcrime_rate<- filter(datastore_resources, row_number()==1) %>% get_resource()

#remove the "geometry" column
my_data <- neighbourhoodcrime_rate  %>% st_set_geometry(NULL)
my_data
```
## Introduction
Statistical analysis is ubiquitous to the Toronto Police Service. The causal links inferred from the criminal rate studies affect police deployment and resident daily life. For instance, based on the collected data, police can catch criminals efficiently, the resident can find a relatively safe region for renting or purchasing a property there. The collected data is accurate and feasible. Therefore, this statistical research report has practical value. 

Logistic regression estimation is widely used for statistical analysis. "In statistics, the logistic model (or logit model) is used to model the probability of a certain class or event existing such as pass/fail, win/lose, alive/dead or healthy/sick"(Wikipedia, "Logistic regression").In this report, this model will be applied to analyze the effects of Neighborhood Crime Rate in the Great Toronto Area.

The rest of the report has three main sections. For the methodology section, the Neighborhood Crime Rates data will be introduced. An appropriate model will be set up. For the result section, the result of some intended statistical analysis will be demonstrated. Summary, conclusion, weakness, and next step are included in the discussion section. 

## Data
The Neighborhood Crime Rate comes from the Toronto Open Data Portal. This data was last refreshed on September 18, 2020, and it refreshes annually by Toronto Police Services, which records the amount of Assault, Auto Theft, Break and Enter, Robbery, Theft Over, and Homicide happened from 2014 to 2019 in 140 regions in Toronto. 

The target population for this report includes all the residents in the Great Toronto Area. The sample is the residents in the 140 regions in the Great Toronto Area. The frame is a list of residents in the 140 regions in the Great Toronto Area. 

The data includes the variables of six crimes count through 2014 to 2019, averages of each crime from 2014-2019, % changes in each crime from 2018-2019, rates of each crime for 2019 per 100,000 population, id number for row identifier, object id (Autogenerated distinct record identifier), name of each Toronto neighborhood, hood id for neighborhood identifier, population from 2016 Census, shape area measurement and shape length measurement on the map.

For this report, the unnecessary columns are omitted. Neighborhood, Population, Assault_2019, Assault_AVG, Assault_Rate_2019, AutoTheft_2019, AutoTheft_AVG, AutoTheft_Rate_2019, BreakandEnter_2019, BreakandEnter_AVG, BreakandEnter_Rate_2019, Homicide_2019, Homicide_AVG, Homicide_Rate_2019, Robbery_2019, Robbery_AVG, Robbery_Rate_2019, TheftOver_2019, TheftOver_AVG, and TheftOver_Rate_2019 are the necessary variables for the study. 

The strength of this data is the data was last refreshed on September 18, 2020, which means the data for 2019 can make the result more reliable. The weakness is that there are only 140 rows; the observations are not very large, which means the result might cause an inaccurate result. 

```{r echo=FALSE}
library(tidyverse)
final_data<-my_data %>%select("Neighbourhood","Population","Assault_2019", "Assault_AVG", "Assault_Rate_2019", "AutoTheft_2019", "AutoTheft_AVG", "AutoTheft_Rate_2019", "BreakandEnter_2019", "BreakandEnter_AVG", "BreakandEnter_Rate_2019", "Homicide_2019", "Homicide_AVG", "Homicide_Rate_2019", "Robbery_2019", "Robbery_AVG", "Robbery_Rate_2019", "TheftOver_2019", "TheftOver_AVG","TheftOver_Rate_2019")
final_data
```
# Reference

1. Open Data Dataset. (2020, September 18). Retrieved September 30, 2020, from https://open.toronto.ca/dataset/neighbourhood-crime-rates/

2. Wickham et al., (2019). Welcome to the tidyverse.
  Journal of Open Source Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686

3. Hadley Wickham, Romain François, Lionel Henry and
  Kirill Müller (2020). dplyr: A Grammar of Data
  Manipulation. R package version 1.0.2.
  https://CRAN.R-project.org/package=dplyr
  
4. Pebesma, E., 2018. Simple Features for R:
  Standardized Support for Spatial Vector Data. The R
  Journal 10 (1), 439-446,
  https://doi.org/10.32614/RJ-2018-009
  
5. "Logistic Regression", Wikipedia, accessed December 21,2020,
https://en.wikipedia.org/wiki/Logistic_regression



